A Geometry for Network Visualization in \MakeLowercase{\texttt{ggplot2}}

### 2015-03-17 CC/writeup.Rnw

\section{Many Many Examples}
\sctq{Format-wise, is it ok if each example is its own subsection?}\\
\sct{
In this section, we demonstrate the capabilities of \texttt{geom\_net} in a series of examples. 
  \subsection{Blood Donation}
  \sctq{I had to comment out all the code chunks for now. Not sure why but it won't compile if they're there.}
  \emph{Note: would be best with labels and direction}\\
  In this network, there are eight nodes and 27 edges.  The nodes represent the eight different blood types possible in humans
%<<blood_ex,highlight=TRUE>>=
%ggplot(data = blood$edges, aes(from_id = from, to_id = to)) + geom_net(vertices = blood$vertices) + expand_limits(x = c(-5,5), y = c(-5,5)) + theme_net #add vlabel later
%@
  \subsection{Email Network}
  \emph{Note: would be best with labels and direction}
% # <<email_ex>>=
% # ggplot(data = email.net, aes(from_id = From, to_id = to, ealpha = 0.1,vsize = 2)) + geom_net(vertices = email.names) + expand_limits(x=c(-1,5), y = c(-1,5)) + facet_wrap(~day) + theme_net
% # @
  \subsection{\texttt{ggplot2} Theme Elements}
  \emph{Note: would be best with labels and direction}
% # <<theme_ex>>=
% # #ggplot(data = g$edges, aes(from_id = child, to_id = parent)) + geom_net(vertices = g$vertices) + expand_limits(x = c(-5,5), y = c(-5,5)) + theme_net
% # @
  \subsection{Madmen Network (again?? or no?)}
  \sctq{leaving blank for now.}
  \subsection{College Football}
  \emph{Note: would be best with coloring vertices by conference} \citet{football}
% # <<football_ex>>=
% # ggplot(data = football$edges, aes(from_id = from, to_id = to)) + geom_net(vertices = football$vertices) + expand_limits(x = c(-2.5,2.5), y = c(-2.5,2.5)) + theme_net
% # @
  \subsection{Les Mis\'{e}rables}
  \emph{Note: data set has edge weightings for number of co-occurences of characters. esize would be useful here!}
% <<lesmis_ex>>=
% ggplot(data = lesmis$edges, aes(from_id = from, to_id = to)) + geom_net(vertices = lesmis$vertices, aes(esize = value), layout = 'fruchtermanreingold') + expand_limits(x = c(-25,25), y = c(-25,25)) + theme_net
% @
}

>>>>

\section{Many Many Examples}
\sctq{Format-wise, is it ok if each example is its own subsection?}\\
\sct{
In this section, we demonstrate the capabilities of \texttt{geom\_net} in a series of examples. 
  \subsection{Blood Donation}
  \sctq{I had to comment out all the code chunks for now. Not sure why but it won't compile if they're there.}
  \emph{Note: would be best with labels and direction}\\
  In this network, there are eight nodes and 27 edges.  The nodes represent the eight different blood types possible in humans
%<<blood_ex,highlight=TRUE>>=
%ggplot(data = blood$edges, aes(from_id = from, to_id = to)) + geom_net(vertices = blood$vertices) + expand_limits(x = c(-5,5), y = c(-5,5)) + theme_net #add vlabel later
%@
  \emph{Note: would be best with labels and direction}
}
<<blood_ex>>=
library(ggplot2) # this needs to be the ggplot2 with geom_net
ggplot(data = blood$edges, aes(from_id = from, to_id = to)) + geom_net(vertices = blood$vertices) + expand_limits(x = c(-5,5), y = c(-5,5)) + theme_net #add vlabel later
@
\sct{
  \subsection{Email Network}
  \emph{Note: would be best with labels and direction}
% # <<email_ex>>=
% # ggplot(data = email.net, aes(from_id = From, to_id = to, ealpha = 0.1,vsize = 2)) + geom_net(vertices = email.names) + expand_limits(x=c(-1,5), y = c(-1,5)) + facet_wrap(~day) + theme_net
% # @
  \subsection{\texttt{ggplot2} Theme Elements}
  \emph{Note: would be best with labels and direction}
% # <<theme_ex>>=
% # #ggplot(data = g$edges, aes(from_id = child, to_id = parent)) + geom_net(vertices = g$vertices) + expand_limits(x = c(-5,5), y = c(-5,5)) + theme_net
% # @
  \subsection{Madmen Network (again?? or no?)}
  \sctq{leaving blank for now.}
  \subsection{College Football}
  \emph{Note: would be best with coloring vertices by conference} \citet{football}
% # <<football_ex>>=
% # ggplot(data = football$edges, aes(from_id = from, to_id = to)) + geom_net(vertices = football$vertices) + expand_limits(x = c(-2.5,2.5), y = c(-2.5,2.5)) + theme_net
% # @
  \subsection{Les Mis\'{e}rables}
  \emph{Note: data set has edge weightings for number of co-occurences of characters. esize would be useful here!}
% <<lesmis_ex>>=
% ggplot(data = lesmis$edges, aes(from_id = from, to_id = to)) + geom_net(vertices = lesmis$vertices, aes(esize = value), layout = 'fruchtermanreingold') + expand_limits(x = c(-25,25), y = c(-25,25)) + theme_net
% @
}
